%-------------------------
% Resume in Latex
% Author : Amlaan Bhoi
% Adapted from: Sourabh Bajaj
% License : MIT
% Modified by : Nicholas Graca 8/12/2020
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}

\usepackage[charter]{mathdesign} % Bitstream Charter
% \usepackage{newpxtext,newpxmath} % Palatino

% Adjust margins
\addtolength{\oddsidemargin}{-0.40in}
\addtolength{\evensidemargin}{-0.40in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBullet}[2]{
  \item[]\small{
    \hspace{-9pt}\textbf{#1}{: #2 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{-10pt}\textbf{#1} & {#2} \\
      \hspace{-10pt}{#3} & {#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% custom commands
\newcommand{\shorterSection}[1]{\vspace{-10pt}\section{#1}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{{\Huge Nicholas Graca}} \\
  \href{mailto:nickgraca@mail.rit.edu}{nickgraca@mail.rit.edu} $\vert$ LinkedIn: \href{https://www.linkedin.com/in/njg7716}{linkedin.com/in/njg7716} $\vert$ Github: \href{https://www.github.com/njg7716}{github.com/njg7716} $\vert$
  508-971-0886
\end{center}
%\bigskip
%-----------SKILLS-----------------
\shorterSection{Technical Skills}
  \resumeSubHeadingListStart
  \normalsize
    \item{
     \textbf{Languages}\small{: Python, Bash, Java, C, MySQL, MIPS Assembly, PowerShell, Go}
     %\hfill
    }\vspace{-10pt}
    \item{
    \textbf{Technologies}\small{: Wireshark, VMware, Git, Docker, Unix, F5, Ansible, Networking, Nginx, Burp, AWS, Web Applications}
    }
    \vspace{-10pt}
\resumeSubHeadingListEnd
%\bigskip
%-----------EXPERIENCE-----------------
\shorterSection{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MIT Lincoln Laboratory | \normalfont{Cyber Security Co-Op}}{May 2021 - August 2021}
      {\vspace{-10pt}}{\vspace{-10pt}}
      \resumeItemListStart
        \resumeItem{Creating Scheduled Tasks}
          {Automated daily email reports on the status of security appliances.}
        \resumeItem{Documentation}
          {Created Standard Operating Procedures documenting how to handle various security incidents.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Constellation Brands Inc. | \normalfont{Risk Management Intern}}{May 2020 - August 2020}
      {\vspace{-10pt}}{\vspace{-10pt}}
      \resumeItemListStart
        \resumeItem{Phishing Training}
          {Assisted in designing phishing training for high risk employees.}
        \resumeItem{SOC Reports}
          {Evaluated SOC reports to ensure that CBI was not taking on unnecessary risk when using third party applications.}
        \resumeItem{Intern projects}
          {Participated in an intern hackathon where I helped develop a web application to recommend recipes after taking a picture of a bottle in AWS. Also worked with interns across various departments to pitch a new product line.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Sherwin-Williams | \normalfont{Application Security Intern}}{May 2019 - December 2019}
      {\vspace{-10pt}}{\vspace{-10pt}}
      \resumeItemListStart
        \resumeItem{Upgrade F5 WAF}
          {Wrote scripts to test F5 functionality after version upgrade}
        \resumeItem{Automate F5}{Used Ansible playbook to automate the deployment of new objects to F5}
        \resumeItem{Audit F5}{All F5 code was in GitHub which allowed us to audit the configuration}
        \resumeItem{Internal Web Application Penetration Test}
        {Performed a manual Penetration Test on an internal application and worked with the developers of the application to remediate vulnerabilities to make us a more secure company and to work along side with and teach Developers how to securely code.}
      \resumeItemListEnd

    \resumeSubheading
      {RIT iSchool Department | \normalfont{Lab Assistant}}{November 2018 - Present}
      {\vspace{-10pt}}{\vspace{-10pt}}
      \resumeItemListStart
        \resumeItem{Work Study Job}{Student job when I am enrolled in classes.}
        \resumeItem{Maintenance}
          {Configured the equipment in the labs for classes and appliance upgrades/replacements to allow students to learn on the most up to date hardware.}
        \resumeItem{Troubleshooting}
          {Help students with their lab if some of the equipment was broken so that they can complete their assignments.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%\bigskip
%-----------PROJECTS-----------------
\shorterSection{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Home Lab}{}{}{}
      \vspace{-20pt}
      \item{\textbf{Honeypot: }}{Configured Raspberry Pi to run SSH and Telnet Honeypot}
      \vspace{-5pt}
      \item{\textbf{Pihole: }}{Setup Pihole DNS Server to block known Ad Domains}
      \vspace{-5pt}
      \item{\textbf{WireGuard VPN: }}{Set Up VPN to remotely access LAN securely}
      \vspace{-5pt}
      \item{\textbf{Speedtest: }}{I was not satisfied with ISP service so I run speedtests through out the day and graph the results}
      %\vspace{-5pt}
  \resumeSubHeadingListEnd
%\bigskip
%-----------EDUCATION-----------------
\shorterSection{Education}
  \resumeSubHeadingListStart
      \resumeSubheading
          {Rochester Institute of Technology}{January 2021 - Present}
          {MS Computing Security}{GPA: 4.0}
    \resumeSubheading
      {Rochester Institute of Technology}{Graduated December 2020}
      {BS Computing Security Minor in Networking and Systems Administration}{GPA: 3.2}
    \resumeSubheading
      {Dean's List: Fall 2018, Spring 2019, Spring 2020, Fall 2020, Spring 2021}{}{}{}{}
      \vspace{-20pt}
  \resumeSubHeadingListEnd
%-----------Additional Experience & Achievements-----------------
\bigskip
\shorterSection{Additional Experience \& Achievements}
  \resumeSubHeadingListStart
  \normalsize
    \item{Member of the RIT Men's Division III Varsity Swimming and Diving team from Fall 2016 to 2019.}
    \vspace{-5pt}
    \item{Member of the RIT Security Club called RITSEC and the RIT Networking Club called NextHop}
    \vspace{-5pt}
    \item{Incident Response Security Competition (IRSEC 3rd Place) - Competed in 2017 and then helped run 2018-Present}
    \vspace{-5pt}
    \item{Information Security Talent Search (ISTS) - Competed in 2017 then helped run 2018-Present}
    \vspace{-5pt}
    \item{Network and Systems Infrastructure Competition (NSIC) - Competed in 2018 and then helped run in 2019}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
